\chapter{Introduction}
\section{Overview}
As we know that Birth/Death Certificates are very essential documents. Birth Certificate can be used as proof of an individual’s age, for academics, for jobs and can be used as an identity for various government documents (Passport, Driving License, Voter-ID, etc.). Likewise, Death Certificates can be used by the family of deceased to inherit property, to claim insurance benefits and used by the government to maintain population statistics. In the current scenario, due to the complex procedure of applying and getting a certificate, nearly half of the world’s population does not have a birth certificate. Also, authentication of a valid certificate is a laborious task. At the same time, due to the presence of hard copy, missing certificates become a crucial problem and re-issuing of that certificate is a hectic process. Presently, the digital certificate is a way to tackle the problem of missing certificates still it is not sufficient as it can tamper easily.
In order to solve this problem,Blockchain provides a common sharing platform for storing,accessing documents and minimizing the overall time for verification and a significant tool to combat document fraud and misuse.


\section{Motivation}
Getting a birth certificate, or any legal identity document, issued in India is often a complex task as one has to go through various levels of bureaucracy and a lot of identity verification and paperwork is required. However, with the help of blockchain technology, our aim is to make it much easier to verify the documents. We hope that with the help of blockchain technology, the process would become more streamlined in terms of handling administrative operations and the process would become simpler and much easier. These Birth and other certificates would be digitally authenticated by issuing authorities (municipalities) and that authentication will be stored on blockchain which facilitates verification of these documents by any third party organization to whom owners provide access. Basically Blockchain would be used to write the hash value of a certificate together with the owner of the certificate and who issued it for the authentication and verification.

\section{Objectives}
We  propose a decentralized system based on blockchain technology, which makes certificate sharing possible while enabling thorough trust among certificate receivers, corresponding issuing authority and end users who will verify the certificate validation by adopting smart contracts without any other systems. \\

In this study, we are going to develop the decentralized certificate verification application on the Ethereum Blockchain.\\ 

We are selecting this blockchain technology because it is immutable, traceable, tamper-proof, encrypted and more secure. \\

By using the blockchain technology we will be able to eradicate the problems like fake certificates and double-spending. \\

Smart contract is at the backend to interact with the blockchain and the encrypted hash value of each certificate will be stored in the blockchain using ipfs. To verify the authenticity of academic certificates the hash value is displayed on a webpage which is retrieved from the blockchain. \\

This blockchain technology has greater transparency, less maintenance and low cost 

\section{Application}
Both the Birth and Death certificates have their importance. In the process of birth/death registration, an individual’s birth/death gets registered in the civil record of a concerned government authority. The birth/death needs to be registered within 21 days. Due to many barriers in the process of birth/death registration, almost half of the world’s population does not register their birth. Furthermore, almost two-thirds of annual deaths are not registered. The challenging task is to verify the Genuinity of the certificate. Currently, there is a manual process to verify the authenticity of the certificates which is time-taking and lengthy. Though, there are chances of producing fake certificates which may be unnoticed by the verifier. Also, there are high chances of forgery and missing certificates as they are in hard copies.
