\addcontentsline{toc}{section}{Synopsis}

\begin{center}
    \underline{\bfseries \huge SYNOPSIS}\\
    \vspace{1cm}
    \end{center}
    Birth and death are two ends of the bridge of life. The two events need to well documented and preserved to honour lives of indivisuals. These documents are used to avail various benefits and are  a proof of life. In today's selfish world we observe that document is forged and exploited to for their gains. Both the Birth and Death certificates are an important individual asset. It gets registered in the civil record of a concerned government authority within 21 days. \newline

There are many barriers in the process of birth/death registration, most of them do  not register their birth. Furthermore, almost two-thirds of annual deaths are not registered. 
The challenging task is to verify the Genuinity of the certificate. Currently, there is a manual process to verify the authenticity of the certificates which is time-taking and lengthy. Though, there are chances of producing fake certificates which may be unnoticed by the verifier. Also, missing certificates as they are in hard copies.\newline
 
We  propose a decentralized system based on blockchain technology, which makes certificate sharing possible while enabling trust among certificate receivers, corresponding issuing authority and end users who will verify the certificate validation by adopting smart contracts without any other systems.\newline
 
We are going to develop a decentralized certificate verification application on the Ethereum Blockchain. By using the blockchain technology we will be able to eradicate the problems like fake certificates and double-spending.
Smart contract is a self executing code which ensures authenticated data is added to the blockchain.  The encrypted hash value of each certificate will be stored in the blockchain using ipfs. Verification of the authenticity of academic certificates is done by checking the presence of the respective ipfs hash value 
\newline
    
    We also aim to take the entire process online where the user can apply online and as per traditions the entire power of issuing these certicates rests in the hands of the local bodies of Municipality or Panchayat respectively
    
